---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addr

<!-- badges: start -->
<!-- badges: end -->

The goal of addr is to clean, parse, harmonize, and hash messy real-world addresses in R.

Addresses that were not validated at the time of collection are often heterogenously formatted, making them difficult to compare or link to other sets of addresses. The addr package is designed to (1) clean character strings of addresses, (2) use the `usaddress` library to tag address components, (3) expand common street type abbreviations, and (4) paste together select components to create a standardized address. Standardized addresses can be hashed to create hashdresses that can be used to merge with other sets of addresses.

## Installation

You can install the development version of addr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("cole-brokamp/addr")
```

## Example

```{r example}
library(addr)
```

Transform messy, real-world addresses into a character vector of standardized address: 

```{r}
addr_standardize(
  x = c(
    "3333 Burnet Avenue Apt 2 Cincinnati OH 45220",
    "3333 bUrNeT Avenue Cincinnati OH 45220",
    "3333 Burnet Avenue Apt #2 Cincinnati OH 45220",
    "3333 Burnet Ave Cincinnati OH 45220",
    "3333 Burnet Av. Cincinnati OH 45220"
  )
)
```

Under the hood, address text is cleaned (`addr_clean()`) and parsed into components (`addr_tag()`). If applicable, the street type abbreviation is expanded (`expand_post_type()`), and the first five digits of the ZIP Code are extracted.

Use `addr_tag()` to generate tagged address components:

```{r}
addr_tag(c("290 Ludlow Avenue Apt #2 Cincinnati OH 45220", "3333 Burnet Ave Cincinnati OH 45219"))
```
