---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/hashdress)](https://CRAN.R-project.org/package=hashdress)
[![R-CMD-check](https://github.com/cole-brokamp/addr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cole-brokamp/addr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# addr

<!-- badges: start -->
<!-- badges: end -->


Addresses that were not validated at the time of collection are often heterogenously formatted, making them difficult to compare or link to other sets of addresses. 
The goal of addr is to clean, parse, and standardize messy, real-world addresses in R to use for further linkage and lookup.

## Installation

You can install the development version of addr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("cole-brokamp/addr")
```

addr requires a working [Rust](https://www.rust-lang.org/learn/get-started) toolchain; install one using [rustup](https://www.rust-lang.org/tools/install).

## Example

```{r example}
library(addr)
```

```{r}
addr_standardize(c("3333 Burnet Ave Cincinnati OH 45219", "202 Riva Ridge Ct Cincinnati OH 45140"))
```
